---
output: github_document
bibliography: simbib.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Reproduce the Analysis from @gerard2022bayesian

[![NSF-2132247](https://img.shields.io/badge/NSF-2132247-blue.svg)](https://nsf.gov/awardsearch/showAward?AWD_ID=2132247)

This repo contains the scripts and instructions to reproduce the results of @gerard2022bayesian. 

## Instructions

To run these scripts, you will need to have the latest version of R and GNU Make.

1. Install the appropriate R packages

    ```{r, eval = FALSE}
    install.packages(c("devtools",
                       "tidyverse",
                       "bench",
                       "ggthemes",
                       "ggpubr",
                       "xtable",
                       "hexbin", 
                       "broom",
                       "patchwork",
                       "foreach",
                       "future",
                       "doFuture",
                       "rngtools",
                       "doRNG"))
    devtools::install_github("dcgerard/hwep")
    devtools::install_github("dcgerard/updog")
    ```
    
2. Run `make` in the terminal.

## Session Information

```{r, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
lapply(c("devtools",
         "tidyverse",
         "ggthemes",
         "ggpubr",
         "hwep",
         "updog",
         "bench",
         "xtable",
         "hexbin",
         "broom",
         "patchwork",
         "foreach",
         "future",
         "doFuture",
         "rngtools",
         "doRNG"), 
       FUN = library,
       character.only = TRUE)
```

```{r, echo = FALSE, comment=""}
sessionInfo()
```

## Acknowledgments

This material is based upon work supported by the National Science Foundation under Grant No. [2132247](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2132247). The opinions, findings, and conclusions or recommendations expressed are those of the author and do not necessarily reflect the views of the National Science Foundation.

# References
